Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-07-08 paper/main.tex
typo

There exist many tools that can automatically derive loops and
recursion bounds for imperative programs such as
SPEED~\cite{GulwaniMC09,GulwaniZ10}, KoAT~\cite{BrockschmidtEFFG14},
PUBS~\cite{AlbertAGPZ12}, Rank~\cite{AliasDFG10},
ABC~\cite{BlancHHK10} and LOOPUS~\cite{Zuleger11,SinnZV14}.  These
tools are based on abstract interpretation--based invariant generation
and/or term rewriting techniques, and they derive impressive results
on realistic software.  The importance of amortization to derive tight
bounds is well known in the resource analysis
community~\cite{AlonsoG12,Moser14,SinnZV14}.  Currently, the only
other available tools that can be directly applied to C code are Rank
and LOOPUS.  Our analysis framework does not aim to set a new standard
for automatic bound analysis.  Our contribution is rather a principled
approach that produces certificates that are proved sound with respect
to a formal cost semantics.  Moreover, we have a system that enables
both automatic and interactive bound derivation, a formal soundness
proof in Coq, and a method that can handle resources that can be
released (e.g., memory).  However, as we have shown
in~\pref{sec:exper}, our automatic amortized analysis matches the
state of the art in automatic bound analysis for linear bounds and
sometimes even derives better constant factors than the other tools.
Since Rank and Loopus do not handle recursion, our automatic amortized
analysis is also the only available tool that can derive bounds for
recursive C programs.

>>>>

There exist many tools that can automatically derive loop and
recursion bounds for imperative programs such as
SPEED~\cite{GulwaniMC09,GulwaniZ10}, KoAT~\cite{BrockschmidtEFFG14},
PUBS~\cite{AlbertAGPZ12}, Rank~\cite{AliasDFG10},
ABC~\cite{BlancHHK10} and LOOPUS~\cite{Zuleger11,SinnZV14}.  These
tools are based on abstract interpretation--based invariant generation
and/or term rewriting techniques, and they derive impressive results
on realistic software.  The importance of amortization to derive tight
bounds is well known in the resource analysis
community~\cite{AlonsoG12,Moser14,SinnZV14}.  Currently, the only
other available tools that can be directly applied to C code are Rank
and LOOPUS.  Our analysis framework does not aim to set a new standard
for automatic bound analysis.  Our contribution is rather a principled
approach that produces certificates that are proved sound with respect
to a formal cost semantics.  Moreover, we have a system that enables
both automatic and interactive bound derivation, a formal soundness
proof in Coq, and a method that can handle resources that can be
released (e.g., memory).  However, as we have shown
in~\pref{sec:exper}, our automatic amortized analysis matches the
state of the art in automatic bound analysis for linear bounds and
sometimes even derives better constant factors than the other tools.
Since Rank and Loopus do not handle recursion, our automatic amortized
analysis is also the only available tool that can derive bounds for
recursive C programs.
